Fast Sorting on Modern Computers

### 2005-08-01 docs/tech_report/conclusions.tex

\section {Branch Results}

@@

Selection sort also has a very low number of branch mispredictions, the results
of which match up well to Knuth's calculation. We found as well that bubblesort
and shakersort have incredibly bad branch prediction performance, bring
$O(N^2)$.

We found a pattern in branch misprediction when using a fanout in our 8-heap,
and that this pattern matched closely that of selection sort, discussed above.

TODO merge

>>>>

\section{Branch Results}
%TODO this section has to be reread by David

@@

Selection sort also has a very low number of branch mispredictions, the results
of which match up well to Knuth's calculation. We found as well that bubblesort
and shakersort have incredibly bad branch prediction performance. Both are
$O(N^2)$ sorts, and the number of branches and branch misses have the same
complexity.
%TODO i dont like how this reads

TODO bubblesort

In heapsort, we found a pattern of branch mispredictions when using a fanout in
our 8-heap, and that this pattern matched closely that of selection sort,
discussed above. Despite this property, the number of mispredictions using an
8-heap was greater than when using a 4-heap.

Using a k-way merge, multi-mergesort had a great number of extra branch
predictions. While many of these were mispredicted using the bimodal predictor,
the 2 level adaptive predictor was able to predict a higher
proportion correctly.
